---
title: "INFO550_Zhihao Jin"
author: "Zhihao Jin"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The preliminary project is to check the missing area of GOES16 aerosol optical depth (AOD) observations in the north-east area of the US.

## Load packages

```{r load_lib, echo=FALSE}
library(data.table)
library(lubridate)
library(reshape2)
library(raster)
library(rasterVis)
library(animation)
```

## Load and combine all .csv data within one day. Use day 001 as an example, all .csv files without any records were not saved.
Observation is recorded every 5 minutes.
lon:Longitude
lat:Latitude
AOD:Aerosol optial depth
DQF:Data quality flag
hour: Observation EST time in hour.

```{r load_combine_data}
dayi="001"
filepath<-paste0("C:/Users/zjin75/OneDrive - Emory University/Emory/LiuGroup/WRF/DATA/GOES_G16/",dayi)
  file_list<-dir(filepath,pattern = ".csv")
  daily_data<-NULL
  for(filei in file_list){
    GOES_nyc<-read.csv(paste0(filepath,"/",filei))
    GOES_nyc<-na.omit(GOES_nyc)
    daily_data<-rbind(daily_data,GOES_nyc)
    
  }
  str(daily_data)
```
## Data clean
1.calculate hourly AOD
2.project into raster

```{r data_clean }
  #calculate the hourly AOD based on the 5-minute AOD data for each point.
  daily_data<-as.data.frame(daily_data)
  daily_data.dcast<-dcast(daily_data,lon+lat~hour,mean,value.var = "AOD",na.rm=T)
  
  #turn NAN into NA
  for(coli in 1:ncol(daily_data.dcast)){
    daily_data.dcast[is.nan(daily_data.dcast[,coli]),coli]<-NA
    daily_data.dcast[,coli]<-as.numeric(daily_data.dcast[,coli])
  }
  
  #change column name into form day_h_hour
  names(daily_data.dcast)[3:ncol(daily_data.dcast)]<-paste0(dayi,"_h_",names(daily_data.dcast)[3:ncol(daily_data.dcast)])
  
  #load the template polygon to fill the data into a teissian polygon and then transform into raster
  load("C:/Users/zjin75/OneDrive - Emory University/Emory/LiuGroup/WRF/DATA/GOES_G16/GOES_Tessian_Polygon.RData")
  daily_poly<-merge(GOES_polygon,daily_data.dcast,by=c("lon","lat"))
  daily.rast<-stack()
  
  #the loop below may take 3 minutes
  for(i in 3:ncol(daily_poly)){
    daily.rast<-stack(daily.rast,rasterize(daily_poly,domain_20degree_grid,names(daily_poly)[i]))
  }
  names(daily.rast)<-names(daily_poly)[3:length(names(daily_poly))]
  

```

## Figures
The figure shows a large missing part both spatially and temporally because the satellite observation is based on the sunlight.It can be interfered by the image angels, weather, cloud, and time.

```{R create_figure}
# load shapefile for US states
shapefile<- getData("GADM", country = "US", level =1)

# create GIF showing all availble hour AOD in the north-east US
  saveGIF({
    for (i in c(1:nlayers(daily.rast))) {
      l<-levelplot(daily.rast[[i]], par.settings = BuRdTheme(), margin=FALSE, main=list(paste0(names(daily.rast)[i]),adj=0,line=0))+
        latticeExtra::layer(sp.polygons(shapefile,col = "black",lwd=2))
      plot(l)
    }
  }, interval=0.5, movie.name=paste0("animation_",dayi,".gif"))
```
